### 2017-09-16 monograph/thesis/postexto/abstracts.tex
Forced wrap lines as 80 characters on abstracts.tex
Created the reference structuredEditorStudy on references.bib and
added its abstract to monograph/thesis/postexto/abstracts.tex

>>>>

    \item \textbf{Study and Creation of a Structured Code Editor}: Virtually all
    of the code editors for business use in general\hyp{}purpose languages are
    oriented to lines and characters. The alternative, editors working directly
    with the syntactic tree, has received most attention in this area, aiming to
    have important advantages, such as automatic control of the structure and
    greater efficiency in the script. The purpose of this paper is to study
    these alternating active editors, called structured editors or syntax-driven
    editors, comparing them with traditional editors. Once the advantages and
    disadvantages have been raised, a structured editor will be developed that
    best fits in with this medium. This work first provides for an in-depth
    study of these structured editors, in the context of programming in general
    or non-general purpose languages. Previous efforts in this area will be
    sought, assessing their impact, lessons learned and limitations encountered.
    In a second moment these lessons will be used for the development of a
    proprietary, fully structured or hybrid editor, in order to increase the
    efficiency of the programmer. Preferably this editor will be prepared for a
    standard general purpose language and will be able to edit actual programs.
    This work aimed to better understand the principles behind structured
    editors, seeking information on their effectiveness, advantages,
    disadvantages and factors involved in their lack of adoption. It is also
    envisaged the construction of a functional structured editor, capable of
    being used on a daily basis, that makes better use of these advantages.
    \cite{structuredEditorStudy}
